Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-12 latex/paper.tex
updated paper

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\caption{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{figure}

@@

\subsubsubsection{Quantum Fibonacci}
The quantum version of Fibonacci was presented in \cite{gilliam2020canonical}. This paper shows that

A versão quântica usada para calcular Fibonacci foi apresentada em \cite{gilliam2020canonical} e  demonstra que, utilizando um circuito do qual coloca em superposição todas as bit-strings com $n$ qubits, e então realizando operações para remover valores que possuem $1$s consecutivos, é possível encontrar o valor $n$ na sequência.

\begin{center}
	\includegraphics[scale=0.3]{fibonacci-circuit.png}
	\captionof{figure}{Exemplo Algoritmo Quântico de Fibonacci}
	\label{fig:fibonacci-circuit}
\end{center}

\begin{center}
	\includegraphics[scale=0.6]{fibonacci-4.png}
	\captionof{figure}{Resultado Fibonacci - F(4)}
	\label{fig:fibonacci-circuit-result}
\end{center}

Após executar o circuito, é necessário verificar a quantidade de bit-strings únicas que apareceram durante os experimentos. No exemplo em \ref{fig:fibonacci-circuit-result}, foram usados $4$ qubits para calcular $F(4)$. Assim, ao contar as bit-strings, temos $F(4) = 8$, retornando então o quarto valor da sequência (nesse caso, a sequência começa do valor $2$, seguindo dessa forma: $F(1)=2, F(2)=3, F(3)=5, F(4)=8, F(5)=13, F(6)=21, ...$). \\
Com isso, é possível usar esse circuito para computações de $F(n)$ utilizando $n$ qubits para encontrar o valor requisitado nessa mesma posição $n$.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\caption{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{figure}

@@

\subsubsubsection{Quantum Fibonacci}

The quantum version of Fibonacci was presented in \cite{gilliam2020canonical}. This paper shows that, using a quantum circuit with all bit-string in superposition, and then apply  controlled rotations to remove values that contains consecutive ones, is possible to approximate the result of the \textit{n}-th Fibonacci sequence value.

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{fibonacci-circuit.png}
	\caption{Quantum Fibonacci Example}
	\label{fig:fibonacci-circuit}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{fibonacci-4.png}
	\caption{Quantum Fibonacci result - F(4)}
	\label{fig:fibonacci-circuit-result}
\end{figure}

After running the circuit $k$ times, the amount of unique bit-string that appeared during the experiment represent the \textit{n}-th Fibonacci value, which $n$ is the total of Qubits were used in the circuit. So, for the example \ref{fig:fibonacci-circuit} above, the position $n$ we want, is $4$, and the result after counting the bars of which values are $\neq 0$ give us the result of $F(4) = 8$.

It may seem wrong, however, the quantum setup differ slightly from the classical one, once the first value is $2$ instead of $1$, this way, the sequence is: $F(1)=2, F(2)=3, F(3)=5, F(4)=8, F(5)=13, F(6)=21, ...$, which implies that it worked for this example.
